MSAD_PCA_Walkthrough

### 2017-02-03 README.Rmd
Changed the lagsIncluded functionality in mspTrain(), the README, and the vignette. Updated the function description to account for these changes. Completed Dr. Hering's edits on mspMonitor(), mspTrain(), and mspWarning().

# Calculate the training summary, but save five observations for monitoring.
trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
                            labelVector = normal_switch_xts[1:(n - 5), 1],
                            trainObs = nTrainObs,
                            lagsIncluded = 1)

>>>>

# Calculate the training summary, but save five observations for monitoring.
trainResults_ls <- mspTrain(data = normal_switch_xts[1:(n - 5), -1],
                            labelVector = normal_switch_xts[1:(n - 5), 1],
                            trainObs = nTrainObs,
                            lagsIncluded = c(0,1))
